True versus apparent shapes of astrophysical bow shocks

### 2016-04-08 papers/Paper1/sec-application.tex
Re-running program to generate variant fits

\begin{figure*}
\begin{tabular}{ccc}
  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV4} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV4} &
  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV4} \\
  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
\end{tabular}
\label{fig:char-radii-obs}
\caption{Examples of shell's circle fit for three sources:177-341, LV5 and 168-328. In the left side, for each source, the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing a 
fraction of the marks, but always keeping at least four points. 177-341 is an example where the measurementsonly change very slightly from one variation to other. While with 168-328 the changes are a little more noticeable. LV4 is a case where the most external points are crucial
in the determination of the radius of curvature}
\end{figure*}

>>>>

\begin{figure*}
\begin{tabular}{@{}c@{}c@{}c@{}}
  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV5} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV5} &
  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV5} \\
  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
\end{tabular}
\label{fig:char-radii-obs}
\caption{Examples of shell's circle fit for three sources:177-341, LV5 and 168-328. In the left side, for each source, the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing a 
fraction of the marks, but always keeping at least four points. 177-341 is an example where the measurementsonly change very slightly from one variation to other. While with 168-328 the changes are a little more noticeable. LV4 is a case where the most external points are crucial
in the determination of the radius of curvature}
\end{figure*}
